Autonomous Quadrotor Landing on a Moving Platform

### 2016-03-07 docs/interim_report/interim_report.tex

\subsubsection*{AprilTag Software}
Using a set of April tags and camera calibration functions provided in the OpenCV library, we been able to successfully obtained accurate pose estimations between the Logitech webcam and a single AprilTag. The translational error in the pose estimation appears to be below $\pm 1$cm while the rotational error has not yet been measured. We plan to use the Optitrack Motion capture system system currently installed in the lab to take a large set of measurements in order to provide an accurate estimation of the errors associated with using the AprilTag Software.

The current rate AprilTag software operates at 20fps on the Odroid and we will investigate a modified version of the AprilTag library made by Kevin Ling, a former Wave Lab member who optimitize the AprilTag source code in a previous project. We have also successfully measured the pose from two April tags simultaneously by placing a small AprilTag inside a larger one such that when the larger AprilTag goes out of the cameras FOV measurements pose estimates will be provided by the smaller one. This has the advantage of continuously providing pose estimation with the quadrotor is less than a meter above the target which is point at which a 40cm by 40cm april tag goes out of the camera view. An example of the two AprilTags providing simultaneous measurements is shown in Figure \ref{fig:apriltag}.

>>>>

\subsubsection*{AprilTag Software}
Using a set of April tags and camera calibration functions provided in the OpenCV library, we been able to successfully obtained accurate pose estimations between the Logitech webcam and a single AprilTag. The translational error in the pose estimation appears to be below $\pm 1$ cm while the rotational error has not yet been measured. We plan to use the Optitrack Motion capture system system currently installed in the lab to take a large set of measurements in order to provide an accurate estimation of the errors associated with using the AprilTag Software.

The current rate AprilTag software operates at 20 fps on the Odroid and we will investigate a modified version of the AprilTag library made by Kevin Ling, a former Wave Lab member who optimitize the AprilTag source code in a previous project. We have also successfully measured the pose from two April tags simultaneously by placing a small AprilTag inside a larger one such that when the larger AprilTag goes out of the cameras FOV measurements pose estimates will be provided by the smaller one. This has the advantage of continuously providing pose estimation with the quadrotor is less than a meter above the target which is point at which a 40cm by 40cm april tag goes out of the camera view. An example of the two AprilTags providing simultaneous measurements is shown in Figure \ref{fig:apriltag}.
